\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-24 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{ComputationalTimeSynthetic.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{20}\times\mathbb{R}^{20}$ for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\label{fig:CompTimeSynthetic}
\end{figure}

>>>>

\begin{figure}[htpb]
\centering
\includegraphics[width=0.9\linewidth]{ComputationalTimeSynthetic.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{20}\times\mathbb{R}^{20}$ for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\label{fig:CompTimeSynthetic}
\end{figure}
\begin{figure}[htpb]
\centering
\includegraphics[width=0.9\linewidth]{RelativeErrorMeanMCVersusProxSynthetic.png}
\caption{\small{The relative error between the empirical mean (i.e., Monte Carlo estimate) $\bm{\mu}_{\text{MC}}\in\mathbb{T}^{20}\times\mathbb{R}^{20}$, and the mean $\bm{\mu}_{\text{Prox}}\in\mathbb{T}^{20}\times\mathbb{R}^{20}$ obtained using the proximal updates of the joint state PDFs, for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\label{fig:CompTimeSynthetic}
\end{figure}
